Technical Report

### 2018-06-22 fully-abstract-comp/technical-report.tex
Remove obsolete definition.
Remove obsolete comment.
More minor cleanups.

\[
  \writeCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad (\lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1) \wedge\\
      \qquad \forall r \in S \ldotp \pwheap(r).H \nsupeq \stdreg{R(r),\gc}{\pur}.H \wedge\\
      \qquad \quad \pwheap(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
\lau{TODO: Make this condition require a set of adjacent regions. Check whether necessary for the stack region.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
% \dominique{Why $n-1$ above?  There is already a quantification over $n' <n$ in the memory satisfaction relation and another $n-1$ is used in $\stdreg{[\baddr',\eaddr'],\gc}{\pur}$. Also: readCond doesn't have the $n-1$. Update: the memory satisfaction was updated by Lau to remove the quantification over $n' < n$ and I dropped the $n-1$ here.}
\[
  \stackWriteCond{W} = \left\{ \npair{A}) \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge \\
      \qquad \forall r \in S \ldotp |R(r)| = 1 \wedge \\
      \qquad \forall r \in S \ldotp \pwfree(r).H \nsupeq \stdreg{R(r),\gc}{\pur}.H \wedge\\
      \qquad \quad \pwfree(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

% \[
%   \execCond{\lin,W} = \left\{ \npair{(S_\perm,\baddr,\eaddr)} \middle|
%     \begin{array}{l}
%       \forall n' < n, W' \privft W, \perm \in S_\perm, \aaddr \in [\baddr,\eaddr] \ldotp\\
%       \quad \forall W'', c_{d,S},c_{d,T} \ldotp \npair[n']{\stpair[.]{c_{d,S}}{c_{d,T}}} \in \lrv(W'') \wedge \\
%       \qquad \npair[n']{[\stpair[.]{((\perm,\lin),\baddr,\eaddr,\aaddr)}{((\perm,\lin),\baddr,\eaddr,\aaddr)},\stpair[.]{c_{d,S}}{c_{d,T}}]} \in \lrp(W' \oplus W'') \Rightarrow \\
%       \quad \qquad \npair[n']{\stpair[.]{((\perm,\lin),\baddr,\eaddr,\aaddr)}{((\perm,\lin),\baddr,\eaddr,\aaddr)},\stpair[.]{c_{d,S}}{c_{d,T}}} \in \lre(W' \oplus W'')
%     \end{array}
%     \right\}
% \]

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
Note: this new version of execCond uses the expression relation for regular jumps since it expresses the validity of jumping to an address pointed to by an executable capability. 
\begin{align*}
  \execCond{W} &=
  \left\{ \npair{A} \middle|
    \begin{array}{l}
      \forall n' < n, W' \future \purePart{W}, \aaddr \in [\baddr',\eaddr'] \subseteq A \ldotp\\
      \quad \npair[n']{\stpair[.]{((\rx,\normal),\baddr',\eaddr',\aaddr)}{((\rx,\normal),\baddr',\eaddr',\aaddr)}} \in \lre(W')
    \end{array}
    \right\}
\end{align*}

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \stdreg{A,\gc}{v} \defeq (v,H_A^{\mathrm{std},\square} \; \gc) , v \in \{\spa,\spao\}
\]
for readability, we use $\spao$ short for $\spatialo$, $\spa$ short for $\spatial$, and $\pur$ as short for $\pure$.
\[
  \stdreg{A,\gc}{\pur} \defeq (\pur,H_A^{\mathrm{std},\square} \; \gc, \lambda \_ \; \_ \ldotp \emptyset)
\]
where $H^{\mathrm{std},\square}_A$ is defined as follows:
\[
  H_A^{\mathrm{std},\square} \; \gc \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \exists S : A \fun \World \ldotp \xi(\hat{W}) = \oplus_{\aaddr \in A} S(\aaddr) \wedge\\
      \quad \forall \aaddr \in A \ldotp \npair{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))
    \end{array}
  \right\}
\]
\lau{01-11-2017: RESOLVED look into what kind of world separation should happen here.}

@@

% \[
%   \staureg{v} = (v,*,=,=,H^{\mathrm{sta},\lrv}_{\stpair{\ms}{\ms}})
% \]
% \[
%   H^{\mathrm{sta},\lrv}_{\stpair{\ms}{\ms}} = 
%     \left\{ \npair{\stpair{\ms}{\ms}} \middle|
%       \begin{array}{l}
%         \exists S : \dom(\ms_S) \fun \World \ldotp \xi(W) = \oplus_{\aaddr \in \dom(\src{\ms_S})} S(\aaddr) \wedge\\        
%         \quad \forall \aaddr \in \dom(\ms) \ldotp \npair[n-1]{\src{\ms_S}(\aaddr),\ms_T(\aaddr)} \in \lrv(S(a))
%       \end{array}
% \right\}
% \]

@@

% \subsection{World specifies component}

% \begin{definition}[World specifies component]
%   We define that a world $W$ specifies the presence of a component with global constants $\gc$
%   \begin{equation*}
%     \var{comp}_0 = (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss,A_\linear)
%   \end{equation*}
%   (written as $W \vdash_\gc \var{comp}_0$)
%   iff there exist $r_1 \cdots r_n \in \dom(\pwheap)$ such that for all $i$,
%   \begin{itemize}
%   \item 
%     \begin{equation*}
%       \vdash (\code_i,\msdata[i],\overline{c_{\mathrm{import},i}},\overline{c_{\mathrm{export},i}},\sigrets_i,\sigcloss_i,A_{\linear,i})
%     \end{equation*}
%   \item $\mscode = \biguplus_i \code_i$
%   \item $\msdata = \biguplus_i \msdata[i]$
%   \item $\overline{c_{\mathrm{export}}} = \biguplus_i \overline{c_{\mathrm{export},i}}$
%   \item $\overline{c_{\mathrm{import}}} = \biguplus_i \overline{c_{\mathrm{import},i}} \setminus \overline{c_{\mathrm{export}}}$
%   \item $\sigrets = \biguplus \sigrets_i$
%   \item $\sigcloss = \biguplus \sigcloss_i$
%   \item $A_\linear = \biguplus A_{\linear,i}$
%   \item $\pwheap(r_i) = \codereg[\mathrm{code}_i,\square]{\sigrets_i,\sigcloss_i,\code_i,\gc}$
%   \item For all $i$, one of the following holds:
%     \begin{itemize}
%     \item $\dom(\code_i) \subseteq \ta$
%     \item $\dom(\code_i) \mathrel{\#} \ta$
%     \end{itemize}
%   \end{itemize}
%   and there exist $r_{\mathrm{addr}} : \dom(\msdata) \mapsto \dom(\pwheap)$ such that
%   \begin{itemize}
%   \item For all $\aaddr\in\dom(\msdata)$, $\pwheap(r_{\mathrm{addr}}(\aaddr)) = \stdreg{\{\aaddr\},\gc}{\lin}$ with ($\lin = \pure$ if $\aaddr\not\in A_\linear$) and ($\lin = \spatialo$ if $\aaddr\in A_\linear$)
%   \end{itemize}
%   with $\gc = (\ta,\stkb)$
% \end{definition}
% Note that for untrusted components, we require all seals to be in the corresponding code region as closure seals.
% That is because we cannot trust untrusted components to treat their seals correctly (e.g. not hand them out to other components, only sign return capabilities with return seals etc.), so instead, they must be considered as closure seals, which the component is essentially allowed to sign anything with.

% \begin{lemma}[World specifies linked component if it specifies each separately]
%   \label{lem:world-specifies-linked}
%   If
%   \begin{itemize}
%   \item $W \vdash_\gc \var{comp}_0$
%   \item $W \vdash_\gc \var{comp}_0'$
%   \end{itemize}
%   Then $W \vdash \var{comp}_{0} \bowtie \var{comp}_{0}'$
% \end{lemma}
% \begin{proof}
%   Follows easily from the definitions.
% \end{proof}

% \begin{lemma}[World specifies component pure]
%   \label{lem:world-specifies-comp-pure}
%   If $W \vdash_\gc \var{comp}_0$ then $\purePart{W} \vdash \var{comp}_{0}$.
% \end{lemma}
% \begin{proof}
%   Follows easily from the definitions.
% \end{proof}

@@

  \begin{definition}[Reasonable pc]
    \label{def:reasonable-pc}
    We say that an executable capability $c =
    ((\perm,\normal),\baddr,\eaddr,\aaddr)$ behaves reasonably up to $n$ steps
    if for any $\Phi$ such that
    \begin{itemize}
    \item $\Phi.\reg(\pcreg) = c$
    \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ and
      free stack $\Phi.\ms_\stk$ for all $r \not\in \{\pcreg\}$
    \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint
    \end{itemize}
    We have that $\Phi$ is reasonable up to $n$ steps.
  \end{definition}

  \begin{definition}[Reasonable component]
    \label{def:reasonable-component}
    We say that a component
    $(\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss,A_\linear)$
    is reasonable if the following hold: For all $\sealed{\sigma,\vsc} \in
    \overline{c_{\mathrm{export}}}$, with $\exec{\vsc}$, we have that $\vsc$
    behaves reasonably up to any number of steps $n$.
    \lau{Is this reasonable as a word? In that case, it should  mention the
      memory and free stack.}
  \end{definition}

>>>>

\[
  \writeCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad (\lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1) \wedge\\
      \qquad \forall r \in S \ldotp \pwheap(r).H \nsupeq \stdreg{R(r),\gc}{\pur}.H \wedge\\
      \qquad \quad \pwheap(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
\lau{TODO: Make this condition require a set of adjacent regions. Check whether necessary for the stack region.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackWriteCond{W} = \left\{ \npair{A}) \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge \\
      \qquad \forall r \in S \ldotp |R(r)| = 1 \wedge \\
      \qquad \forall r \in S \ldotp \pwfree(r).H \nsupeq \stdreg{R(r),\gc}{\pur}.H \wedge\\
      \qquad \quad \pwfree(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\dominique{22-6-2018: address-stratified is useless for length-one regions.}

Note: this new version of execCond uses the expression relation for regular jumps since it expresses the validity of jumping to an address pointed to by an executable capability. 
\begin{align*}
  \execCond{W} &=
  \left\{ \npair{A} \middle|
    \begin{array}{l}
      \forall n' < n, W' \future \purePart{W}, \aaddr \in [\baddr',\eaddr'] \subseteq A \ldotp\\
      \quad \npair[n']{\stpair[.]{((\rx,\normal),\baddr',\eaddr',\aaddr)}{((\rx,\normal),\baddr',\eaddr',\aaddr)}} \in \lre(W')
    \end{array}
    \right\}
\end{align*}

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \stdreg{A,\gc}{v} \defeq (v,H_A^{\mathrm{std},\square} \; \gc) , v \in \{\spa,\spao\}
\]
for readability, we use $\spao$ short for $\spatialo$, $\spa$ short for $\spatial$, and $\pur$ as short for $\pure$.
\[
  \stdreg{A,\gc}{\pur} \defeq (\pur,H_A^{\mathrm{std},\square} \; \gc, \lambda \_ \; \_ \ldotp \emptyset)
\]
where $H^{\mathrm{std},\square}_A$ is defined as follows:
\[
  H_A^{\mathrm{std},\square} \; \gc \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \exists S : A \fun \World \ldotp \xi(\hat{W}) = \oplus_{\aaddr \in A} S(\aaddr) \wedge\\
      \quad \forall \aaddr \in A \ldotp \npair{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))
    \end{array}
  \right\}
\]

@@

@@

@@

  \begin{definition}[Reasonable pc]
    \label{def:reasonable-pc}
    We say that an executable capability $c =
    ((\perm,\normal),\baddr,\eaddr,\aaddr)$ behaves reasonably up to $n$ steps
    if for any $\Phi$ such that
    \begin{itemize}
    \item $\Phi.\reg(\pcreg) = c$
    \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ and
      free stack $\Phi.\ms_\stk$ for all $r \neq \pcreg$
    \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint
    \end{itemize}
    We have that $\Phi$ is reasonable up to $n$ steps.
  \end{definition}

  \begin{definition}[Reasonable component]
    \label{def:reasonable-component}
    We say that a component
    $(\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss,A_\linear)$
    is reasonable if the following hold: For all $\sealed{\sigma,\vsc} \in
    \overline{c_{\mathrm{export}}}$, with $\exec{\vsc}$, we have that $\vsc$
    behaves reasonably up to any number of steps $n$.
    % \lau{Is this reasonable as a word? In that case, it should  mention the
    %   memory and free stack.}
    % \dominique{No: this is reasonable as a pc.}
  \end{definition}
